---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

#### import data
```{r}
library(classdata)
library(ggplot2)
library(dplyr)
```

## 1. inspect the first few lines of the data set:
```{r}
?ames
names(ames)
dfAmes <- classdata::ames
head(dfAmes)
```
- There are 16 variables. These include Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea(sf), Bedrooms, FinishedBsmtArea(sf), LotArea(sf), AC, FirePlace, and Neighborhood. You can find data on the meaning and range of the variables by running the code.


## 2. is there a variable of special interest or focus?

- Since the main varible for exploration is Sales Price, we want to look at variables that would likely influence the price. Of the 16, we think Acres, YearBuilt, TotalLivingArea, and Bedrooms would be variables worth looking at that would likely effect the Sales Price.

## 3. start the exploration with the main variable:
```{r}
ggplot(ames, aes(x = `Sale Price`)) + geom_histogram(binwidth = 100000)
```

- The range of the variable Sale Price is between 0 and 20,500,000. A vast majority of the housing price falls between 0 and 200,000. There's a fair amount of outliers roughly in the million to 2 million range for housing price.

## 4. pick a variable that might be related to the main variable.


